\documentclass{llncs}

\usepackage{llncsdoc}

\pagestyle{plain}
\usepackage{graphicx}
\usepackage[english]{babel}
\usepackage{blindtext}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{bm}
\usepackage{multirow}
\usepackage{amsmath}
\usepackage{mathtools}
\usepackage{mathrsfs}
\usepackage{theorem}
\usepackage{amsfonts,amssymb}
\usepackage{multicol}
\usepackage{diagbox}
\usepackage[misc]{ifsym}
%\usepackage[noend]{algpseudocode}


\usepackage{extarrows}

\usepackage{algorithm}

\usepackage{float}
\usepackage{xspace}
\usepackage[inline]{enumitem}



%\let\llncssubparagraph\subparagraph
%\let\subparagraph\paragraph
%\usepackage[compact]{titlesec}
%\let\subparagraph\llncssubparagraph


%\bibliographystyle{alpha}
\bibliographystyle{splncs03}




%\usepackage{geometry}
%\geometry{a4paper,left=2cm,right=2cm,top=3cm,bottom=3cm}





\usepackage[pdfstartview=FitH,
bookmarksnumbered=true,bookmarksopen=true,
colorlinks=true,pdfborder=001,citecolor=blue,
linkcolor=blue,urlcolor=blue]{hyperref}
\begin{document}


\pagenumbering{arabic}

\renewcommand\theenumi{\roman{enumi}}
\renewcommand\labelenumi{(\theenumi)}
\newcommand\xiao[1]{{\color{red}[xiao: #1]}}

\input{macros.tex}





\title{Beyond-Birthday-Bound Security for (Tweakable) Linear SP-networks}


%\author{\today}
\urldef{\mails}\path|18340823418@163.com,chun.guo@sdu.edu.cn,mqwang@sdu.edu.cn|
\author{Yuan Gao\inst{1,2} \and Chun Guo\inst{1,2 \text{(\Letter)}} \and Meiqin Wang\inst{1,2 \text{(\Letter)}}}
\institute{Key Laboratory of Cryptologic Technology and Information Security of Ministry of Education, Shandong University, Qingdao, Shandong, 266237, China,    \and
School of Cyber Science and Technology, Shandong University, Qingdao, Shandong, China    \\
\mails
}


%\date{\today}
\maketitle



%%-------------------------------------- Abstract -------------------------------------------------------------
\begin{abstract}
Recent works (Cogliati et al., CRYPTO 2018) have initiated provable security analysis of Substitution-Permutation Networks (SPNs), one of the most popular approach to construct modern blockciphers. In this theoretical model, the diffusion layers may be {\it non-linear}, which enables beyond-birthday-bound provable security. Though, for the SPN model with {\it linear diffusion layers}, which is closer to real world blockciphers, existing provable results are capped at the birthday barrier.

This paper solves this open problem, and proves that a 4-round SPN with linear diffusion layers is secure up to $2^{2n/3}$ adversarial queries. Besides, we show how to tweak linear SPNs and prove the 6-round tweakable linear SPN is beyond birthday security. This provides additional insights into the real world SPN ciphers.
\end{abstract}

\begin{keywords}
Blockcipher \and Provable security \and Key-alternating cipher \and Substitution-Permutation networks \and  domain extension of block ciphers \and beyond-birthday-bound
\end{keywords}

%\tableofcontents


%\input{chapters/ch1-introduction.tex}

\input{chapters/ch2-preliminary.tex}

\input{chapters/ch3-related-work.tex}

\input{chapters/ch4-4-round-proof.tex}

\input{chapters/ch5-tweakable-linear-SPN.tex}





\section*{Acknowledgements}

Chun Guo was partly supported by the Program of Qilu Young Scholars (Grant No. 61580089963177) of Shandong University.
Weijia Wang was partly supported by the Program of Qilu Young Scholars of Shandong University.
Meiqin Wang was supported by ...


\bibliography{reference-set,crypto/abbrev3,crypto/crypto}

\newpage
\begin{center}
\bf\huge Supplementary Material
\end{center}
\vspace{5pt}
%{\small
\appendix
%\section{4 Rounds with Rate 1/2}
%\label{sec:on-4-rounds-sprp}
%\input{sections/app-sprp-4-rounds}

%}

\end{document}
